---
title: "seafood"
author: "Alan Nurcahyo"
date: "9/5/2020"
output: pdf_document
---

```{r message=FALSE}
#library used
library(tidyverse)
library(caret)
library(quanteda)
library(doSNOW) #run model to run in each core
library(cld3)
library(googleLanguageR)
library(irlba)
library(class)
```

# Preprocessing
## Load and review dataset
```{r}
#load dataset
df <- read_csv("/Users/alannurcahyo/Documents/Documents/AU/fall2020/DATA/Seafood_Dishes.csv")
##check label
unique(df$seafood_yn) 

#create labeled dataset
df.labeled <- df %>%
  filter(seafood_yn %in% c(0,1))
prop.table(table(df.labeled$seafood_yn))

#create unlabeled dataset
df.unlabeled <- df %>%
  filter(!seafood_yn %in% c(0,1))

head(df)

```
Evaluate distribution of labeled and non labeled by Year
```{r}
#Histogram of first time the menu appeared
# It appears that the labeled data lack of observation from later year
df %>%
  filter(first_appeared != 0,
         first_appeared != 1,
         first_appeared != 2928) %>%
  mutate( seafoonTF = !is.na(seafood_yn)) %>%
  ggplot(aes(first_appeared, fill = seafoonTF)) + 
  geom_histogram(binwidth = 10)

#Histogram of last time the menu appeared
# It appears that the labeled data has a sufficient range of observation
df %>%
  filter(last_appeared != 0,
         last_appeared != 1,
         last_appeared != 2928) %>%
  mutate( seafoonTF = !is.na(seafood_yn)) %>%
  ggplot(aes(last_appeared, fill = seafoonTF)) + 
  geom_histogram(binwidth = 10)

# comparison between labeled and unlabeled data by first appeared
# It appears that labeled data lack of observation after 1908 
count.first.appeared <- df %>%
  filter(first_appeared != 0,
         first_appeared != 1,
         first_appeared != 2928) %>%
  mutate( seafoodTF = !is.na(seafood_yn)) %>%
  group_by(first_appeared, seafoodTF) %>%
  count() %>%
  spread(seafoodTF, n)

# number of unlabeled observation after 1098 
sum(count.first.appeared$`FALSE`[count.first.appeared$first_appeared>1907])

# number of labeled observation after 1098 
sum(count.first.appeared$`TRUE`[count.first.appeared$first_appeared>1907], na.rm = TRUE)

# let's take one percent of oberservation after 1908 to be labeled and round it
# per year we need following observation
n_new_sample <- count.first.appeared %>%
  mutate(n_sample = round(`FALSE`/100,0)) %>%
  select(first_appeared,n_sample) %>%
  filter(first_appeared >1907,
         n_sample >0)

## we take n number of observation from unlabeled dataset by following the number we need on n_new_sample$n_sample
new_sample <- vector(mode = "list", length = nrow(n_new_sample))
for (i in seq_along(new_sample)) {
  new_sample[[i]] <- df.unlabeled %>%
    filter(first_appeared == n_new_sample$first_appeared[[i]]) %>%
    sample_n(n_new_sample$n_sample[[i]])
}
new_sample <- do.call(rbind, new_sample)

# write it to csv
# write_csv(new_sample,"new_sample.csv")
# label it manually, then load the labeled new sample into R
new_sample_labeled <- read_csv("new_sample_labeled.csv")
new_sample_labeled <- new_sample_labeled %>%
  filter(seafood_yn %in% c(0,1))
```

Translate
```{r}
############### detect langauage use cld3 #################### 
df.labeled.cld3 <- df.labeled%>%
  mutate(name = str_to_lower(name),
         lang = cld3::detect_language(name))

###################### use google API #########################
## the output file is saved in .csv because it is costly and time consuming to run it everytime
# gl_auth("seafood-translation-f329aa685c7f.json")
# df.name.translate <- vector(mode = "list", length = nrow(df.labeled))
# 
# for (i in seq_along(df.name.translate)) {
#      df.name.translate[[i]] <- gl_translate(df.labeled$name[i], target = "en")
# }
# 
# df.name.translate.bind <- do.call(rbind, df.name.translate)
# prop.table(table(df.name.translate.bind$detectedSourceLanguage))
# 
# write.csv(df.name.translate.bind,"NameTranslated.csv")
df.name.translate.bind <- read_csv("NameTranslated.csv")
# 
# # translate new_sample_labeled
# gl_auth("seafood-translation-2ae5d5055080.json")
# df.name.translate.newsample <- vector(mode = "list", length = nrow(new_sample_labeled))
# #
# for (i in seq_along(df.name.translate.newsample)) {
#       df.name.translate.newsample[[i]] <- gl_translate(new_sample_labeled$name[i], target = "en")
# }
# 
#  df.name.translate.newsample <- do.call(rbind, df.name.translate.newsample)
df.name.translate.newsample <- read_csv("new_sample_translated.csv")
 
##use translated as our dataset
df.labeled <- cbind(df.labeled, df.name.translate.bind)
df.labeled <- df.labeled %>%
  dplyr::select(-text , -X1, -description)
## for new sample
new_sample_labeled <- cbind(new_sample_labeled, df.name.translate.newsample)
new_sample_labeled <- new_sample_labeled %>%
  dplyr::select(-text, -description)

## bind with new labeled dataset
df.labeled <- rbind(df.labeled, new_sample_labeled)

## check distribution
#Histogram of first time the menu appeared
df.labeled %>%
  filter(first_appeared != 0,
         first_appeared != 1,
         first_appeared != 2928) %>%
  mutate( seafoonTF = !is.na(seafood_yn)) %>%
  ggplot(aes(first_appeared, fill = seafoonTF)) + 
  geom_histogram(binwidth = 10)

# comparison between labeled and unlabeled data by first appeared
count.first.appeared <- df.labeled %>%
  filter(first_appeared != 0,
         first_appeared != 1,
         first_appeared != 2928) %>%
  mutate( seafoodTF = !is.na(seafood_yn)) %>%
  group_by(first_appeared, seafoodTF) %>%
  count() %>%
  spread(seafoodTF, n)


## Comparation between cld3 and GoogleAPI  -- googleAPI is outperform cld3 in language detection

df.name.translate.bind %>%
  group_by(detectedSourceLanguage) %>%
  tally() %>%
  arrange(desc(n)) %>%
  mutate(prop = n/nrow(df.name.translate.bind)) %>%
  slice(1:5) %>%
  ggplot(aes(detectedSourceLanguage,prop)) + geom_col() +
  theme_bw() + labs(title = "top 5 language by google")

df.labeled.cld3 %>%
  group_by(lang) %>%
  tally() %>%
  arrange(desc(n)) %>%
  mutate(prop = n/nrow(df.name.translate.bind)) %>%
  slice(1:5) %>%
  ggplot(aes(lang,prop)) + geom_col() +
  theme_bw() + labs(title = "top 5 language by cld3")



### adding new variable to df.labeled to improve model performance
popularseafoodwords <- c("oyster", "Oyster", "crab","Crab", "clam", "Clam","lobster","Lobster")
popularseafoodwords <- paste(popularseafoodwords,collapse = "|")
df.labeled <- df.labeled %>%
  mutate(popseafood = ifelse(str_detect(translatedText,popularseafoodwords),1,0),
         digit4 = ifelse(str_detect(translatedText,"[:digit:]{4}"),1,0))
```

# create training and test

```{r}
set.seed(1234)

#create index of stratified 70:30 split that maintain proportion of label.
index <- caret::createDataPartition(df.labeled$seafood_yn, times = 1,
                                    p = 0.7, list= FALSE) 

# train and test
train <- df.labeled[index,]
test <- df.labeled[-index,]

##verify
prop.table(table(train$seafood_yn))
prop.table(table(test$seafood_yn))

```


## preprocess training set
### preprocess training set using only noun as data frame
```{r}

############## choosing only Noun ##############
## annotate dish name

library(udpipe)
dl <- udpipe_download_model(language = "english")
udmodel<- udpipe_load_model(file = dl$file_model)
annotate <- udpipe_annotate(udmodel, train$translatedText)
annotate <- as.data.frame(annotate)
table(annotate$upos)
Noun <- annotate %>%
  filter(upos == "NOUN") %>%
  dplyr::select(token)
Noun <- Noun[1:nrow(Noun),]
Noun <- unique(Noun)

#create a corpus
corpus <- corpus(train$translatedText) 

#create document frequency matrix with verb
dfm.train <- dfm(corpus, 
             tolower=TRUE,  
             remove_punct =TRUE, 
             remove_numbers=TRUE,
             remove_symbols = TRUE,
             remove_hyphens = TRUE,
             remove=stopwords('english', source = "snowball"), 
             stem=TRUE, 
             verbose=TRUE)
dfm.train.Noun <- dfm_select(dfm.train, pattern = Noun)
dim(dfm.train.Noun)

##setup feature dataframe with label
train.dfm <- data.frame(label=as.factor(train$seafood_yn), 
                        popseafood = train$popseafood, 
                        digit4 = train$digit4,
                        dfm.train.Noun) %>%
  select(-document)
head(train.dfm)
```
### preprocess training set using all words then convert it to 300 variable using svd
```{r}
#create a corpus
corpus <- corpus(train$translatedText) 

#create document frequency matrix with verb
dfm.train <- dfm(corpus, 
             tolower=TRUE,  
             remove_punct =TRUE, 
             remove_numbers=TRUE,
             remove_symbols = TRUE,
             remove_hyphens = TRUE,
             remove=stopwords('english', source = "snowball"), 
             stem=TRUE, 
             verbose=TRUE)

dim(dfm.train)

############## make TF-IDF version of data ##################
## make tf function
term.frequency <- function(row){
  row/sum(row)
}

## make function to calculate IDF
inverse.doc.freq <- function(col) {
  corpus.size <- length(col)
  doc.count <- length(which(col>0))
  log10(corpus.size/doc.count)
}

## make function to calculate tf/idf

tf.idf <- function(tf,idf) {
  tf*idf
}

## make tf matrix transformation 
dfm.train.tf <- apply(dfm.train, 1, term.frequency)
dim(dfm.train)

## make idf . NOTe: This IDF will be used again later in test dataset
dfm.train.idf <- apply(dfm.train, 2, inverse.doc.freq)

## make tf-idf matrix 
dfm.train.tfidf <- apply(dfm.train.tf, 2, tf.idf, idf = dfm.train.idf)
dim(dfm.train.tfidf)

## transpose t-idf matrix
dfm.train.tfidf <- t(dfm.train.tfidf)
dim(dfm.train.tfidf)
view(dfm.train.tfidf[1:20,1:100])

## check incomplete cases -- it is possible that with our preprocessing some dish 
## have name that being removed
incomplete.cases <- which(!complete.cases(dfm.train.tfidf))
train$translatedText[incomplete.cases]

## fix it
dfm.train.tfidf[incomplete.cases,] <- rep(0.0, ncol(dfm.train.tfidf))

################ end of tf-idf ##################


########## Singular value decomposition ##########

## record start time
start.time <- Sys.time()

### perform SVD to decrease dimentionality  to 300 using package irlba
train.irlba <- irlba(t(dfm.train.tfidf), nv = 300, maxit = 600)

## total time ~12 minutes
total.time <- Sys.time() - start.time 


## save svd value for test data
sigma.inverse <- 1/train.irlba$d
u.transpose <- t(train.irlba$u)

##setup feature dataframe with label

train.svd <- data.frame(label=as.factor(train$seafood_yn), 
                        popseafood = train$popseafood, 
                        digit4 = train$digit4,
                        train.irlba$v)
dim(train.svd)

save(train.svd,file = "trainingsvd.Rdata")
load("trainingsvd.Rdata")
head(train.svd)
################# end of SVD ###################################
```

## preprocessing test
### preprocess test set using only noun as data frame
```{r}

############## choosing only Noun ##############
#create a corpus
corpus <- corpus(test$translatedText) 

#create document frequency matrix with verb
dfm.test <- dfm(corpus, 
             tolower=TRUE,  
             remove_punct =TRUE, 
             remove_numbers=TRUE,
             remove_symbols = TRUE,
             remove_hyphens = TRUE,
             remove=stopwords('english', source = "snowball"), 
             stem=TRUE, 
             verbose=TRUE)
dfm.test.Noun <- dfm_select(dfm.test, pattern = dfm.train.Noun)
dim(dfm.train.Noun)

############### setup feature dataframe with label   #####################
test.dfm <- data.frame(label=as.factor(test$seafood_yn), 
                       popseafood = test$popseafood, 
                       digit4 = test$digit4, 
                       dfm.test.Noun) %>%
  select(-document)
```

### preprocess test set using all words then convert it to 300 variable using svd
```{r}
#create a corpus
corpus <- corpus(test$translatedText) 


#create document frequency matrix in a go
dfm.test <- dfm(corpus, 
             tolower=TRUE,  
             remove_punct =TRUE, 
             remove_numbers=TRUE,
             remove_symbols = TRUE,
             remove_hyphens = TRUE,
             remove=stopwords('english', source = "snowball"), 
             stem=TRUE, 
             verbose=TRUE)

### convert test data set to have the samee dimension as training data ##
dfm.test <- dfm_select(dfm.test, pattern = dfm.train)
dfm.test.matrix <- as.matrix(dfm.test)
dim(dfm.test)

############## make TF-IDF version of data ##################

## make tf matrix transformation 
dfm.test.tf <- apply(dfm.test.matrix, 1, term.frequency)


## make tf-idf matrix using idf from training data, 
## because we expect that any new document that comes in the future has to
## correspondent with our main corpus (training data)
dfm.test.tfidf <- apply(dfm.test.tf, 2, tf.idf, idf = dfm.train.idf)
dim(dfm.test.tfidf)

## transpose t-idf matrix
dfm.test.tfidf <- t(dfm.test.tfidf)
dim(dfm.test.tfidf)

## check incomplete cases -- it is possible that with our preprocessing some dish 
## have name that being removed
incomplete.cases <- which(!complete.cases(dfm.test.tfidf))

## fix it
dfm.test.tfidf[incomplete.cases,] <- rep(0.0, ncol(dfm.test.tfidf))

################ end of tf-idf ##################


########## Singular value decomposition ##########

test.svd <- t(sigma.inverse*u.transpose %*% t(dfm.test.tfidf))

############### setup feature dataframe with label   #####################
test.svd <- data.frame(label=as.factor(test$seafood_yn), 
                       popseafood = test$popseafood, 
                       digit4 = test$digit4, 
                       test.svd)
dim(test.dfm)

save(test.svd,file = "testsvd.Rdata")

system("say just finished")

################# end of SVD ###################################
```

## model performance evaluation
```{r}
## create a function to determine best model
best.accuracy <- function(result, testdf) {
  accuracy <- 1:length(result)
  n.test <- nrow(testdf)
  for (i in seq_along(result)) {
    accuracy[[i]] <- sum(testdf$label == result[[i]] )/n.test 
  }
  CPR <- max(accuracy)
  k <- which.max(accuracy)
  conf.matrix <- confusionMatrix(as.factor(result[[k]]),testdf$label)
  best.model <- list(max_correct_predicted_rate =CPR,
                     best_thershold = k,
                     best_confusion.matric = conf.matrix)
  return(best.model)
}
```



## use KNN

```{r}
######### knn #########################

# KNN is a non-parameteric classification method where in order to predict a response class
# we use the value of k-nearest neighbour in the data set. k indicate the number of neighbour we want to 
# use in the model. The distance between neighbour is determined using Euclidean Distance


################# use 10-fold cv ######################
# use caret package to make stratified 10-fold cross validation repeated
# # create index to 10-fold cv, use ROC as a model selection criteria
# cv.control <- trainControl(method = "cv", number = 10, 
#                            summaryFunction = twoClassSummary,
#                            classProbs = TRUE)
# 
# # time the code execution
# start.time <- Sys.time()
# 
# # knnFit <- train(label ~ ., data = train.svd, 
# #                 method = "knn", 
# #                 trControl = cv.control, 
# #                 preProcess = c("center","scale"), 
# #                 tuneLength = 10)
# 
# total.time <- Sys.time() - start.time
## Took about 3 hours to train the model
# ## save(knnFit,file = "knnFit.Rdata")
# load("knnFit.Rdata")
# knnFit
# plot(knnFit)

##################### using simple test and training ##################

################ using dfm version of data ###########


set.seed(1234)
knn.result <- knn(train.dfm,test.dfm,train.dfm$label, k = 1)

best.accuracy(knn.result,testdf = test.dfm)
system("say just finished")



########### ends of model using dfm version of data ##################


################ using svd version of data ###########
knn.result <- vector(mode = "list",length=5)
tune.knn <- c(3,5,10,25,50)

set.seed(1234)
for (i in seq_along(tune.knn)) {
  knn.result[[i]] <- knn(train.svd,test.svd,train.svd$label, k = tune.knn[i])
}



best.accuracy(knn.result,testdf = test.svd)
system("say just finished")

########### ends of model using svd version of data ##################
```


## use logistic regression

```{r}
#using simple test and training, we previously use cross validation but ends up too long
############# using svd version of data #########
# time the code execution
start.time <- Sys.time()

logfit <- glm(label ~ ., data = train.svd, family=binomial)

total.time.train.log <- Sys.time() - start.time

## Took less than a minute to return a model
total.time.train.log

##################### predict with test ##################
# predict
logpredict <- predict(logfit, newdata = test.svd,  type = "response")
log.result <- vector(mode = "list",length=100)

## generate list with different threshold
for (i in 1:100) {
  log.result[[i]] <- 1*(logpredict > i/100 )
}

## determine best model
best.accuracy(log.result, testdf = test.svd)
system("say just finished")


############# using dfm version of data #########
# time the code execution
start.time <- Sys.time()

logfit <- glm(label ~ ., data = train.dfm, family=binomial)

total.time.train.log <- Sys.time() - start.time

## Took less than a minute to return a model
total.time.train.log

##################### predict with test ##################
# predict
logpredict <- predict(logfit, newdata = test.dfm,  type = "response")
log.result <- vector(mode = "list",length=100)

## generate list with different threshold
for (i in 1:100) {
  log.result[[i]] <- 1*(logpredict > i/100 )
}

## determine best model
best.accuracy(log.result, testdf = test.dfm)
system("say just finished")
```

# try to use original high dimention data with log regression
```{r}
train.noverb <- data.frame(label = as.factor(train$seafood_yn), dfm.train)
train.noverb <- train.noverb %>%
  dplyr::select(-document)

test.noverb <- data.frame(label = as.factor(test$seafood_yn), dfm.test)
test.noverb <- test.noverb %>%
  dplyr::select(-document)

set.seed(1234)
# use caret package to make stratified 10-fold cross validation repeated
# use caret package to make stratified 10-fold cross validation repeated

cv.folds <- createMultiFolds(train.noverb$label, k = 10, times = 2)
cv.control <- trainControl(method = "repeatedcv", number = 10,
                           repeats = 2, index = cv.folds)

# time the code execution
start.time <- Sys.time()

noverb.logFit <- train(label ~ ., data = train.noverb, 
                method = "glm", 
                family=binomial(),
                trControl = cv.control, 
                tuneLength = 10)

total.time.train.log.noverb <- Sys.time() - start.time


## Took o train the model
total.time
save(allvar.logFit,file = "allvar.logFit.Rdata")


##################### predict with test ##################
# time the code execution
start.time <- Sys.time()
# predict
allvar.logFit <- predict(allvar.logFit, newdata = test.tfidf )

total.time.predict.log.allvar <- Sys.time() - start.time

confusionMatrix(allvar.logFit, test.tfidf$label )
```

# make models use random forest 
## use R default setting - Error: protect(): protection stack overflow 
## - try to tweak default R setting: Error: vector memory exhausted (limit reached?)
## solution to try: use machine with bigger memory
```{r}
# set.seed(1234)
# 
# cv.folds <- createMultiFolds(train$seafood_yn, k = 10, times = 1)
# cv.control <- trainControl(method = "repeatedcv", number = 10,
#                            repeats = 1, index = cv.folds)
# 
# cl <- DoSNOW::makeCluster(20)
# registerDoSNOW(cl)
# 
# # time the code execution
# start.time <- Sys.time()
# 
# # build decision tree - rpart
# rpart.cv.1 <- train(label~.,data = train.svd, 
#                     method = "rf",
#                     trcontrol = cv.control,
#                     tuneLength = 10)
# 
# total.time <- Sys.time() - start.time
# 
# DoSNOW::stopCluster(cl)
load("trainingrf.Rdata")
rf.cv.1
# rfpredict <- predict(rf.cv.1, newdata = test.svd)
load("rfpredict.rdata")
confusionMatrix(rfpredict, test.svd$label)
```
